Untitled

### 2020-05-13 tour-vis.Rmd
modify polish; new tour path plot; new data for geo search

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache= TRUE)
library(tidyverse)
library(ferrn)
library(patchwork)
library(ggrepel)

load(here::here("data/temp.rda"))
load(here::here("data/data_mult.rda"))
load(here::here("data/holes_1d_geo.rda"))
load(here::here("data/holes_2d_geo.rda"))
load(here::here("data/holes_2d_better.rda"))
load(here::here("data/holes_2d_better_random.rda"))
load(here::here("data/holes_2d_geo_polish.rda"))
load(here::here("data/holes_2d_better_polish.rda"))
load(here::here("data/holes_2d_better_random_polish.rda"))

load(here::here("data/interrupt_yes.rda"))
load(here::here("data/interrupt_no.rda"))
```

@@

Guided tour creates visualisation for the projections found by projection pursuit by constructing a tour path. An illustration from @buja2005computational entails the geodesic interpolation bewteen the plane generated by projection pursuit.

![](figures/tour-path.png)

@@

```{r eval = FALSE}
set.seed(123456)
temp <- animate_dist(data, tour_path = guided_tour(holes(), d = 1,
                                           search_f =  search_geodesic),
                  rescale = FALSE, verbose = TRUE)

@@

```{r echo = TRUE}
temp %>% head(5)
```

@@

```{r echo = TRUE}
holes_2d_geo %>% explore_trace_all()
```

@@

```{r echo = TRUE}
holes_2d_geo %>% explore_trace_interp()
holes_2d_better %>% explore_trace_interp()
```

@@

In principle, all the optimisation routines should present the same output on the same problem. In Figure \@ref(fig:trace-compare), red dots shows the trace of the interpolated basis using three different methods on the 2D projection problem. We can observe that different optimisation methods attains different ending index value. This motivates the creation of a polishing search that polishes the ending basis and achieves unity on different methods.

@@

After polishing, all three methods attain the same index value as shown in Figure \@ref(fig:trace-compare). This allows us to evaluate the performance of each searching method. Search_better_random finds an ending basis with a decent high index value while search_geodesic and search_better don't and make search polish do a large proportion of the work.

```{r trace-compare, fig.cap="Breakdown of index value when using different searching methods in conjunction with search polish. All three methods attain the same index value after the polishing. Search better random finds a decent ending basis while search better and search geodesic don't and search polish has done a large proportion of polishing."}
p1 <- bind_rows(holes_2d_geo, holes_2d_geo_polish) %>% 
  explore_trace_interp(point = TRUE) + ggtitle("search_geodesic")

p2 <- bind_rows(holes_2d_better, holes_2d_better_polish) %>% 
  explore_trace_interp(point = TRUE) + ggtitle("search_better")

p3 <- bind_rows(holes_2d_better_random, holes_2d_better_random_polish) %>% 
  explore_trace_interp(point = TRUE) + ggtitle("search_better_random")

(p1 | p2 | p3) &
  theme(legend.position = "none") 
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
library(tidyverse)
library(ferrn)
library(patchwork)
library(ggrepel)

load(here::here("data/temp.rda"))
load(here::here("data/data_mult.rda"))
load(here::here("data/holes_1d_geo.rda"))
load(here::here("data/holes_2d_geo.rda"))
load(here::here("data/holes_2d_better.rda"))
load(here::here("data/holes_2d_better_max_tries.rda"))
load(here::here("data/holes_2d_better_random.rda"))
load(here::here("data/holes_2d_geo_polish.rda"))
load(here::here("data/holes_2d_better_polish.rda"))
load(here::here("data/holes_2d_better_max_tries_polish.rda"))
load(here::here("data/holes_2d_better_random_polish.rda"))
load(here::here("data/interrupt_yes.rda"))
load(here::here("data/interrupt_no.rda"))
```

@@

Guided tour creates visualisation for the projections found by projection pursuit by constructing a tour path. An illustration modified from @buja2005computational entails the geodesic interpolation bewteen the plane generated by projection pursuit.

![](figures/tour_path.svg)

@@

```{r eval = FALSE}
set.seed(123456)
holes_1d_geo <- animate_dist(data, tour_path = guided_tour(holes(), d = 1,
                                           search_f =  search_geodesic),
                  rescale = FALSE, verbose = TRUE)

@@

```{r echo = TRUE}
holes_1d_geo %>% head(5)
```

@@

The tracing plot is useful to explore the index value. Given a global object created, `explore_trace_all()` plots the index value of all the bases.

```{r echo = TRUE}
holes_2d_geo %>% explore_trace_all(magnify = TRUE)
holes_2d_geo %>% explore_trace_interp()
```

@@

@@

In principle, all the optimisation routines should present the same output on the same problem. In Figure \@ref(fig:trace-compare), red dots shows the trace of the interpolated basis using `search_geodesic` and `search_better` (with max.tries = 100), respectively, on the 2D projection problem. We can observe that they attain slightly different ending index value, which is not ideal. This motivates the creation of a polishing search that polishes the ending basis and achieves unity on different methods.

```{r}
p1 <- bind_rows(holes_2d_geo, holes_2d_geo_polish) %>% 
  explore_trace_interp(point = TRUE) + ggtitle("search_geodesic")

p2 <- bind_rows(holes_2d_better_max_tries, holes_2d_better_max_tries_polish) %>% 
  explore_trace_interp(point = TRUE) + ggtitle("search_better")

(p1 | p2) &
  theme(legend.position = "none") 
```

@@

The following example conducted a 2D projection on the larger dataset using search better with different configurations. `max.tries` is a hyperparameter that controls the maximum number of try without improvement and its default value is 25. As shown in Figure \@ref(fig:trace-compare), after polishing, both trials attain the same index value. However, a small `max.tries` of 25 is not sufficient for the algorithm to find the true maximum. This is because 25 tries is not sufficient for the 2D searching space.

```{r trace-compare, fig.cap="Breakdown of index value when using different max.tries in search better in conjunction with search polish. Both attain the same final index value after the polishing while using a max.tries 25 is not sufficient to find the ture maximum."}

p1 <- bind_rows(holes_2d_better, holes_2d_better_polish) %>% 
  explore_trace_interp(point = TRUE) + ggtitle("max.tries = 25")

p2 <- bind_rows(holes_2d_better_max_tries, holes_2d_better_max_tries_polish) %>% 
  explore_trace_interp(point = TRUE) + ggtitle("max.tries = 500")

(p1 | p2) &
  theme(legend.position = "none") 
```
